---
title: "hello world"
description: |
  Taking the `radix` R package for a test spin with `Scikit Learn`!
author:
  - name: Jixing Liu
    url: https://jixing.netlify.com/
    affiliation: DeepDrug
    affiliation_url: http://www.deepdrug.cn/en/
date: "`r Sys.Date()`"
output: radix::radix_article
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,      # Output code chunks
    message = FALSE,  # Toggle off message output 
    warning = FALSE)  # Toggle off warning output
library(DataPackageR)
pkg_path <- getwd()
```

## 1. Create a data package directory structure.
```{r}
datapackage_skeleton(name = "ddDataSets",
                     path = pkg_path,
                     force = TRUE)
```



## 2. Add raw data to the package.
```{r}
# write our raw data to a csv
write.csv(
  x = cars ,
  file = file.path(pkg_path, "cars.csv"),
  row.names = FALSE
)

# this works because we called datapackage_skeleton() first.
use_raw_dataset(file.path(pkg_path, "cars.csv"))

```

## 3. Add a data processing script.
```{r}
use_processing_script(file = "tidy_cars.Rmd",
                      author = "Jixing Liu",
                      title = "Process cars into tidy_cars.")
```

## 4. Edit your processing script.


## 5. Let DataPackageR know about the data objects to store in the package.
```{r}
use_data_object("tidy_cars")
```



## 6. Build the package (for the first time).

```{r}
options("DataPackageR_interact" = FALSE)
package_build(packageName = file.path(pkg_path, "ddDataSets"),
              install = FALSE)

```


## 7. Next edit the data set documentation.

```{r}
# edit this documentation.R file in raw_data
# ensure we run document() from the DataPackageR namespace and not document() from roxygen or devtools.
package_path <- file.path(pkg_path,"ddDataSets")
DataPackageR::document(package_path)
```

## 📌  Iterate: repeat the 2-7 

We can add more data sets, more scripts, and so forth, until we’re happy with the package.

## 8. A Filnal Build

```{r}
package_build(file.path(pkg_path,"ddDataSets"))
```

## git and github

cd the package file
use git to push to github



## 8. links:

+ [rOpenSci | Building Reproducible Data Packages with DataPackageR](https://ropensci.org/blog/2018/09/18/datapackager/)
